### 2022-11-14 NSF2022/Description/summary.tex
summary updated

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis and numerical simulations of
collective dynamics and self-assembly arising from attractive
interactions between dipolar/nematic particles in a suspension. 
%
%One example is the organization of lipids and proteins in vesicles, which is crucial
%to design effective drug carriers. 
%
Physicists model such a self-assembly
using particles possessing a biphasic material label on either half,
with one more hydrophobic than the other. Hydrophobic surfaces
experience a non-additive long-range attraction called the hydrophobic
force. This force is a major source of nonspecific interactions in
biology and soft matter. Despite its ubiquity, theoretical developments
explaining its basic underlying principles have come relatively late.
Motivated by its broad applicability, the PIs recently developed a novel
and intuitive mathematical model, called the hydrophobic attraction
potential model, based on the linear response of water to surface
perturbations. This model was used to show, for the first time,
self-assembly of such bipolar particles into vesicle-like structures
using moving domain elliptic partial differential equations.

@@

The PIs propose to analyze the near-linear elliptic PDEs, develop fast and accurate numerical schemes, 
and apply their hydrophobic attraction potential model to
more general self-organization dynamics. They aim to generalize the
linear-response model to  a wider class of hydrophobic interactions, and
numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on 
the kinetic theory to investigate the rheological properties of the assembly of 
particles with tunable hydrophobicity. The unifying
aspects of the project are establishing a platform for efficiently
simulating the collective dynamics at large scales, and the focusing on
rigorous, mathematical analysis of the underlying model equations and
complicated geometries. The project supports undergraduate and graduate
student collaborators.

>>>>

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis, and
numerical simulations of collective dynamics and self-assembly arising
from attractive interactions between dipolar/nematic particles in a
suspension. Physicists model such a self-assembly using particles
possessing a biphasic material label on either half, with one more
hydrophobic than the other. Hydrophobic surfaces experience a
non-additive long-range attraction called the hydrophobic force. This
force is a major source of nonspecific interactions in biology and soft
matter. Despite its ubiquity, theoretical developments explaining its
basic underlying principles have come relatively late.  Motivated by its
broad applicability, the PIs recently developed a novel and intuitive
mathematical model, called the hydrophobic attraction potential model,
based on the linear response of water to surface perturbations. This
model was used to show, for the first time, self-assembly of such
bipolar particles into vesicle-like structures using moving domain
elliptic partial differential equations (PDEs).

@@

The PIs propose to analyze the elliptic PDEs, develop fast and accurate
numerical algorithms, and apply their hydrophobic attraction potential
model to more general self-organization dynamics. They aim to generalize
the linear-response model to a wider class of hydrophobic interactions,
and numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on
the kinetic theory to investigate the rheological properties of the
assembly of particles with tunable hydrophobicity. The unifying aspects
of the project will establish a platform for efficiently simulating
the collective dynamics of large numbers of particles, and focus on
rigorous, mathematical analysis of the underlying model equations in
complex geometries. The project supports undergraduate and graduate
student collaborators.
